Phenotype and risk factors of venom-induced anaphylaxis: a case-control study of the European Anaphylaxis Registry

### 2019-12-19 analysis/paper/paper.Rmd
minor correction in fig e 3

---
title: "Phenotype and risk factors of venom-induced anaphylaxis: a case - control study of the European Anaphylaxis Registry"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/american-medical-association.csl" # Insert path for the bib-style
---

@@

ggarrange(
  ggarrange(
  cardiac_masto_plots[[6]]+
              labs(x = "cardiac arrest",
                   fill = "mastocytosis"),
  #hypotension2,
  #  nrow = 1,
  #  ncol = 2
age_sex_matched %>% group_by(grouping,atopy) %>% dplyr::count() %>%
  filter(!is.na(atopy)) %>%
  ggpubr::ggbarplot(
    x = "atopy",
    y = "n",
    fill = "grouping",
    palette = palBW,
    position = position_fill()
  )+
  annotate("text", x = 1.5,y = .5,label = "*",size= 9)),
cramV,
nrow = 2, 
ncol = 1
#widths = c(1,1.8)
)
```

>>>>

---
title: "Phenotype and risk factors of venom-induced anaphylaxis: a case-control study of the European Anaphylaxis Registry"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    #bookdown::html_document2:
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/american-medical-association.csl" # Insert path for the bib-style
---

@@

ggarrange(
  ggarrange(
  cardiac_masto_plots[[6]]+
              labs(x = "cardiac arrest",
                   fill = "mastocytosis"),
  #hypotension2,
  #  nrow = 1,
  #  ncol = 2
age_sex_matched %>% filter(grouping=="insects") %>% 
  mutate(age_g = ifelse(d_age <22,"<22",">21")) %>% 
  filter(q_114_hypotension_collapse_v5!="unknown") %>% 
  group_by(age_g,q_114_hypotension_collapse_v5) %>% dplyr::count() %>%
  ggpubr::ggbarplot(
    fill = "q_114_hypotension_collapse_v5",
    y = "n",
    x = "age_g",
    palette = palBW,
    position = position_fill()
  )+
  labs(x = "age group [years]", fill = "hypotension")+
  annotate("text", x = 1.5,y = .5,label = "*",size= 9)),
cramV,
nrow = 2, 
ncol = 1
#widths = c(1,1.8)
)
```
